\large{\bf Looking forwards and backwards through locally regulated populations }

### 2023-03-22 forwards-and-backwards.tex
minor edits

It is convenient to characterise the process as a solution to a martingale problem.
We write $C_b^\infty(\IR^d)$ for the space of bounded smooth functions on $\IR^d$, and, where
convenient, we
write $\langle f, \eta \rangle = \int_{\IR^d} f(x) \eta(dx)$.
\begin{definition}[Martingale Problem Characterisation]
    \label{defn:mgale_construction}
	For each value of $N$ and $\theta$, and each purely atomic 
$\eta_0^N\in\measures$ with atoms of mass $1/N$,
$(\eta^N_t)_{t \geq 0}$ is the (scaled) empirical measure of a birth-death 
process with c\`adl\`ag paths in $\measures$ for which,
for all $f \in C^{\infty}_{b}(\IR^d)$,
writing $q_\theta(x, dy)$ for the Gaussian kernel
with mean $x + \meanq(x)/\theta$ and covariance $\covq(x) / \theta$,
\begin{equation}
    \label{eqn:eta_martingale}
\begin{aligned}
M^N_t(f)
&:=  \langle f, \eta^N_t \rangle
        -\langle f, \eta^N_0 \rangle
 \\ &\qquad {}
 -  \int_{0}^{t}\bigg\{
        \bigg\langle \left( \int \theta
             \left(
                f(z)r(z, \eta^N_{s})
                - f(x)r(x, \eta^N_{s})
            \right)
        q_\theta(x,dz) \right)
%\\ & \qquad \qquad \qquad \qquad {}
         \gamma(x, \eta^N_{s}), \eta^N_{s}(dx) \bigg\rangle
\\ & \qquad \qquad \qquad \qquad \qquad {}
    + \bigg\langle f(x) F(x, \eta^N_{s}),
    \eta^N_{s}(dx) \bigg\rangle
    \bigg\} ds
\end{aligned}    
\end{equation}
is a martingale (with respect to the natural filtration), 
with quadratic variation
    \begin{equation} \label{eqn:prelimit_martingale_variation}
\begin{aligned} \relax
[ M^N(f)]_t =& 
\frac{\theta}{N} \int_{0}^{t}\bigg\{
    \Big\langle \gamma(x, \eta^N_{s})
        \int f^2(z)r(z, \eta^N_{s}) q_\theta(x,dz) 
    , \eta^N_{s}(dx) \Big\rangle \\
& \qquad \qquad {}
    + \Big\langle \mu_\theta(x, \eta^N_{s}) f^2(x) 
    , \eta^N_{s}(dx)\Big\rangle
    \bigg\}ds. 
\end{aligned}    
\end{equation}
\end{definition}
The form of~(\ref{eqn:eta_martingale}) and~(\ref{eqn:prelimit_martingale_variation})
is explained in Section~\ref{sec:heuristics}.
Note that since (juvenile) individuals are produced at rate $N \gamma \eta$, but each
has mass $1/N$,
these factors of $N$ cancel in~\eqref{eqn:eta_martingale}. 
Under our scaling, $N$ and $\theta=\theta(N)$ will tend to infinity in such a 
way that $\alpha:=\lim_{N\to\infty}\theta(N)/N$ exists and is finite.
From the expression~(\ref{eqn:prelimit_martingale_variation}) it is easy to guess that 
whether the limiting processes will be deterministic or stochastic
is determined by whether $\alpha$ is zero or nonzero.

@@

In this section we present formal proofs of our 
three
scaling limits. In
Subsection~\ref{sec:population_density_proof} 
we prove Theorem~\ref{thm:nonlocal_convergence}, to obtain a limit in
which interactions between individuals in the population are nonlocal.
In Subsection~\ref{subsec:nonlocal to local}
we show how, in two important examples in which the nonlocal
limit is respectively a deterministic solution to a non-local equation of 
reaction diffusion type and a deterministic solution to a nonlocal 
porous medium equation with an additional logistic growth term, 
one can pass to a further 
limit to obtain a classical PDE. In 
Subsection~\ref{subsec:one step convergence proof}
we prove our third scaling limit, in which 
we pass from our population model 
directly to a reaction diffusion equation without going via a nonlocal
limit.

\comment{TODO add sentences about the sections Peter is editing}

@@

\begin{proof}
Consider the semimartingale decomposition from equation~\eqref{eqn:eta_martingale}:
\begin{align} \label{eqn:eta_f_mgale_decomp}
    \langle f, \eta^N_t \rangle
    &=
    \langle f, \eta^N_0 \rangle
    + \int_0^t \int_{\IR^d} \big\{
        \gamma(x, \eta^N_s) B_f(x, \eta^N_s)
        + f(x) F(x, \eta^N_s)
        \big\} \eta^N_s(dx) ds
    + M^N_t(f) ,
\end{align}
where $M^N_t(f)$ is a martingale
and $B_f$ is defined in \comment{TODO REFER}.
% and we are defining
% \begin{equation}
% \label{generator Bf}
%     B_f(x, \eta) = \int_{\IR^d} \theta (f(y) r(y, \eta) - f(x) r(x, \eta)) q_\theta(x, dy) .
% \end{equation}

@@

We wish to characterise the limit points of
$\{(\eta^{N}_t)_{t>0}\}_{N\geq 1}$ as solutions to a martingale problem 
with generator $\Pgen^{\infty}$ which we now identify. Most of the work
was done in Section~\ref{sec:heuristics}.
First, we record an equivalent formulation
of the martingale problems.
% that follows by application of Dynkin's formula.

\begin{lemma}
    \label{def: MP definition of limit}
\comment{TODO: define $\mathcal{P}^N$ also here.}
For $G \in \mathcal{C}^{\infty}(\IR)$ with $\|G'''\|_\infty<\infty$,
and 
$f \in \mathcal{C}_{b}^\infty(\overline{\IR}^d)$, define the 
function $G_f$ by 
$G_f(\eta):=G (\langle f, \eta \rangle)$.
Let $\Pgen^\infty$ be the generator
given by
\begin{equation}
    \label{eq: Limit Generator Definition}
\begin{aligned}
\Pgen^{\infty} G_f(\eta):=& G'(\langle f, \eta \rangle)
                   %\times 
\left\{
                   \big\langle
                        \gamma(x, \smooth{\gamma} \eta(x))
                            \mathcal{B}\left(
                            f(\cdot) r(\cdot, \smooth{r} \eta(\cdot))
                            \right)(x)
                    +
                    f(x)
                        F(x, \smooth{F} \eta(x)),
                        \eta(dx)
                    \big\rangle
                   \right\}\\
                &+ \frac{\alpha}{2} G''(\langle f, \eta \rangle)
                  %\times 
\left\{
                  \big\langle
                    2\gamma\left( x, \eta \right)
                    r\left(x,\eta \right)
                    %+\mu\left(x,\eta \right)
                    f^2(x),
                    \eta (dx)
                    \big\rangle 
                  \right\}.
\end{aligned}    
\end{equation}
A process $(\eta^{\infty}_t)_{t \geq 0}$ 
is a solution to the $(A, \lp_0)$-martingale problem of Definition~\ref{defn:limiting_lookdown_mgale}
if and only if it is a solution 
to the $(\Pgen^{\infty}, \eta_0)$-martingale problem, i.e.,
if for all such test functions 
$$
    M_t :=
    G_f(\eta^{\infty}_t)-G_f(\eta_0)
    - \int_{0}^{t}\Pgen^{\infty}G_f(\eta^{\infty}_s)ds
$$
is a martingale (with respect to the natural $\sigma$-field). 
\end{lemma}

@@

\comment{I haven't turned the $\mu$ into $\mu_\theta$ below this point.}

% % % % % % % % % % % % %
\section{Lookdown Proofs}

@@

\begin{lemma}
        \label{lem:h_containment}
    Let $h$ be a positive, continuous, nonincreasing, differentiable function on $[0, \infty)$
    such that
    $\int_0^\infty \int_u^\infty h(v) dv du$,
    $\int_0^\infty u^2 |h'(u)| du$,
    and $\int_0^\infty h(u)^2 du$
    are all finite,
    Then under the assumptions of Lemma~\ref{lem:compact containment lookdown},
    \comment{MOVE ASSUMPTIONS HERE}
    for any $T$ there exists a constant $K(T)$ such that for all $M > 0$,
    $$ 
    \limsup_{N \to \infty} \IP\left\{ \sup_{0 \le t \le T} \langle h, \lp^N_t \rangle > M \right\}
    <
    \frac{K(T)}{M} .
    $$
\end{lemma}

@@

\begin{lemma}
    \label{lem:compact containment hn}
    Suppose $f \in C(\bar \IR^d \times [0, \infty))$ and there is a $u_f$ such that
    $f(x, u) = 0$ for all $x$ and $u \ge u_f$.
    Under the assumptions of Lemma~\ref{lem:compact containment lookdown},
    for any $T$ there exists a constant $K(f,T)$ such that for all $M > 0$,
    $$ 
    \limsup_{N \to \infty} \IP\left\{ \sup_{0 \le t \le T} \langle f, \lp^N_t \rangle > M \right\}
    <
    \frac{K(f,T)}{M} .
    $$
\end{lemma}

@@

\begin{lemma}[Compact containment for $\lp$] \label{lem:compact containment lookdown}
    Let $f_1, f_2, \ldots$ be a sequence of functions each satisfying the conditions
    of Lemma~\ref{lem:compact containment hn}.
    Under Assumptions~\ref{def:model_setup},
    if $\theta/N \to \alpha$ and $\lp_0^N \to \lp_0$ weakly as $N \to \infty$,
    where each $\lp_0^N$ is conditionally uniform given $\eta_0^N$
    in the sense of \eqref{eqn:conditionally_uniform}
    and $\lp_0$ is conditionally uniform given $\eta_0$
    in the sense of \eqref{eqn:conditionally_poisson},
    then for any $T$ and $\delta > 0$ there exists a sequence
    $(C_1, C_2, \ldots)$ of finite constants such that
    \begin{align} \label{eqn:compact eqn lookdown}
    \limsup_{N \to \infty}
    \IP\left\{
        \sup_{0 \le t \le T} \langle f_k, \lp^N_t \rangle > C_k
        \text{ for some } k \ge 1
    \right\}
    < \delta .
    \end{align}
\end{lemma}

@@

\begin{definition}
    \label{def2: MP definition of pre-limit}
Let $F \in \mathcal{C}^{2}(\IR)$ and $f \in \mathcal{C}_{0}(\IR^d)$.
We define $\Pgen^N$ to be a generator
acting on test functions of the form
$F_f(\eta):=F (\langle f, \eta \rangle)$
such that 
\begin{equation}
\begin{aligned}
\Pgen^{N} F_f(\eta):=& \int_{\IR^d} \theta\gamma(x, \eta) \left\{\int_{\IR^d} \left\{F(\langle f, \eta \rangle + f(y)/N )-F(\langle f, \eta \rangle )\right\}r(y, \eta)q_{\theta}(x,dy)\right\}N\eta(dx)\\
&+\int_{\IR^d} \theta \mu(x, \eta) \left\{F(\langle f, \eta \rangle - f(x)/N )-F(\langle f, \eta \rangle )\right\}N\eta(dx).
\end{aligned}    
\end{equation}
In this case, our pre-limit model $(\eta^{N}(t))_{t \geq 0}$ is the solution to the Martingale Problem $(\Pgen^{N}, \eta_0)$, i.e. 
for all $F \in \mathcal{C}^{2}(\IR)$
and $f \in \mathcal{C}_{0}(\IR^d)$,
$$M_t:=F_f(\eta^{N}_t)-F_f(\eta_0)
-\int_{0}^{t}\Pgen^{N}F_f(\eta^{N}_s)ds$$
is a martingale, and the initial condition is distributed as a Poisson measure with mean measure $\eta_0$.
\end{definition}

@@

We may now rewrite $\mathcal{P}^NF(\langle f, \eta \rangle)$ as 
\small
\begin{equation} 
    \label{eq: Pre-Limit Generator Expanded}
\begin{aligned}
\Pgen^{N} F_f(\eta):=& F'(\langle f, \eta \rangle)\int_{\IR^d}  \theta\left\{\int_{\IR^d} \left\{f(y)\gamma(x, \eta) r(y,\eta) -f(x)\mu(x, \eta)\right\}q_{\theta}(x,dy)\right\}\eta(dx)\\
&+\frac{1}{2}\frac{\theta}{N}F''(\langle f, \eta \rangle)\int_{\IR^d} 
 \left\{\gamma(x, \eta)\int_{\IR^d} \left\{f^2(y) r(y,\eta) \right\}q_{\theta}(x,dy)+f^2(x)\mu(x, \eta)\right\}\eta(dx)\\
&+\frac{1}{6}\frac{\theta}{N^2}\int_{\IR^d}\left\{ 
F'''(w) \left\{\gamma(x, \eta)\int_{\IR^d} f^3(y) r(y,\eta) q_{\theta}(x,dy)\right\}-F'''(v)f^3(x)\mu(x, \eta)\right\}\eta(dx)
\end{aligned}    
\end{equation}
\normalsize
for some $w,v \in [\langle f,\eta \rangle - ||f||/N, \langle f,\eta \rangle + ||f||/N]$.

As $N\to \infty$, 
$\theta/N \to \alpha$, 
$\theta/N^2 \to 0$,
and 
$$\int_{\IR^d} f^m(y) r(y,\eta) q_{\theta}(x,dy) \to f^m(x)r(x, \eta)$$
for $m=2,3$,
the third term in Equation \eqref{eq: Pre-Limit Generator Expanded} vanishes
while the second term converges to
that of Equation \eqref{eq: Limit Generator Definition}.
Furthermore,
$\mu(x,\eta) = r(x,\eta)\gamma(x,\eta)-\frac{1}{\theta}F(x,\eta) \to r(x,\eta)\gamma(x,\eta),$
so $f^2(x)\mu(x,\eta) \to r(x,\eta)\gamma(x,\eta) f^2(x)$.

Finally, by Equation \eqref{mean measure},
\eqref{eqn:rewritten mean measure}, \eqref{eqn:near_critical} and
\eqref{limit of mean measure equation},
we have 
\begin{multline}
 \theta\left\{\int_{\IR^d} \left\{f(y)\gamma(x, \eta) r(y,\eta) -f(x)\mu(x, \eta)\right\}q_{\theta}(x,dy)\right\}
 \\
\to \gamma(x, \eta)                           \mathcal{B}\left(
                            f(\cdot) r(\cdot, \eta)
                            \right)(x)
                    +
                    f(x)
                        F(x, \eta),
\end{multline}
so comparing terms we have
\begin{equation}
\lim_{N\to \infty} |\mathcal{P}^{N}F\langle f, \eta \rangle - \mathcal{P}^{\infty}F\langle f, \eta \rangle| \to 0,   
\end{equation}
and so by Dominated Convergence Theorem,
we establish Equation 
\eqref{eq: Convergence of Spatial Generator}
which concludes our proof.
\end{proof}

>>>>

It is convenient to characterise the process as a solution to a martingale problem.
We write $C_b^\infty(\IR^d)$ for the space of bounded smooth functions on $\IR^d$, and, where
convenient, we
write $\langle f, \eta \rangle = \int_{\IR^d} f(x) \eta(dx)$.

\begin{definition}[Martingale Problem Characterisation]
    \label{defn:mgale_construction}
	For each value of $N$ and $\theta$, and each purely atomic 
$\eta_0^N\in\measures$ with atoms of mass $1/N$,
$(\eta^N_t)_{t \geq 0}$ is the (scaled) empirical measure of a birth-death 
process with c\`adl\`ag paths in $\measures$ for which,
for all $f \in C^{\infty}_{b}(\IR^d)$,
writing $q_\theta(x, dy)$ for the Gaussian kernel
with mean $x + \meanq(x)/\theta$ and covariance $\covq(x) / \theta$,
\begin{equation}
    \label{eqn:eta_martingale}
\begin{aligned}
M^N_t(f)
&:=  \langle f, \eta^N_t \rangle
        -\langle f, \eta^N_0 \rangle
 \\ &\qquad {}
 -  \int_{0}^{t}\bigg\{
        \bigg\langle \left( \int \theta
             \left(
                f(z)r(z, \eta^N_{s})
                - f(x)r(x, \eta^N_{s})
            \right)
        q_\theta(x,dz) \right)
%\\ & \qquad \qquad \qquad \qquad {}
         \gamma(x, \eta^N_{s}), \eta^N_{s}(dx) \bigg\rangle
\\ & \qquad \qquad \qquad \qquad \qquad {}
    + \bigg\langle f(x) F(x, \eta^N_{s}),
    \eta^N_{s}(dx) \bigg\rangle
    \bigg\} ds
\end{aligned}    
\end{equation}
is a martingale (with respect to the natural filtration), 
with quadratic variation
    \begin{equation} \label{eqn:prelimit_martingale_variation}
\begin{aligned} \relax
[ M^N(f)]_t =& 
\frac{\theta}{N} \int_{0}^{t}\bigg\{
    \Big\langle \gamma(x, \eta^N_{s})
        \int f^2(z)r(z, \eta^N_{s}) q_\theta(x,dz) 
    , \eta^N_{s}(dx) \Big\rangle \\
& \qquad \qquad {}
    + \Big\langle \mu_\theta(x, \eta^N_{s}) f^2(x) 
    , \eta^N_{s}(dx)\Big\rangle
    \bigg\}ds. 
\end{aligned}    
\end{equation}
\end{definition}
The form of~(\ref{eqn:eta_martingale}) and~(\ref{eqn:prelimit_martingale_variation})
is explained in Section~\ref{sec:heuristics}.
Note that since (juvenile) individuals are produced at rate $N \gamma \eta$, but each
has mass $1/N$,
these factors of $N$ cancel in~\eqref{eqn:eta_martingale}. 
Under our scaling, $N$ and $\theta=\theta(N)$ will tend to infinity in such a 
way that $\alpha:=\lim_{N\to\infty}\theta(N)/N$ exists and is finite.
From the expression~(\ref{eqn:prelimit_martingale_variation}) it is easy to guess that 
whether the limiting processes will be deterministic or stochastic
is determined by whether $\alpha$ is zero or nonzero.

@@

In the following sections we present formal proofs of our three scaling limits.
In Subsection~\ref{sec:population_density_proof} 
we prove Theorem~\ref{thm:nonlocal_convergence}, to obtain a limit in
which interactions between individuals in the population are nonlocal.
In Subsection~\ref{subsec:nonlocal to local}
we show how, in two important examples in which the nonlocal
limit is respectively a deterministic solution to a non-local equation of 
reaction diffusion type and a deterministic solution to a nonlocal 
porous medium equation with an additional logistic growth term, 
one can pass to a further 
limit to obtain a classical PDE.
In Section~\ref{subsec:one step convergence proof}
we prove our third scaling limit, in which 
we pass from our population model 
directly to a reaction diffusion equation without going via a nonlocal limit.
Finally, in Section~\ref{sec:lookdown_proofs} we prove our results concerning both convergence of the lookdown representation
and characterization of the lineage process in the deterministic case.

@@

\begin{proof}
Consider the semimartingale decomposition from equation~\eqref{eqn:eta_martingale}:
\begin{align} \label{eqn:eta_f_mgale_decomp}
    \langle f, \eta^N_t \rangle
    &=
    \langle f, \eta^N_0 \rangle
    + \int_0^t \int_{\IR^d} \big\{
        \gamma(x, \eta^N_s) B_f(x, \eta^N_s)
        + f(x) F(x, \eta^N_s)
        \big\} \eta^N_s(dx) ds
    + M^N_t(f) ,
\end{align}
where $M^N_t(f)$ is a martingale and $B_f$ is defined in \ref{generator Bf}.

@@

We wish to characterise the limit points of
$\{(\eta^{N}_t)_{t>0}\}_{N\geq 1}$ as solutions to a martingale problem 
with generator $\Pgen^{\infty}$ which we now identify. Most of the work
was done in Section~\ref{sec:heuristics}.
First, we record an equivalent formulation
of the martingale problems,
which were essentially laid out in Subsection~\ref{sec:population_heuristics}.
% that follows by application of Dynkin's formula.

\begin{lemma}
    \label{def: MP definition of limit}
For $G \in \mathcal{C}^{\infty}(\IR)$ with $\|G'''\|_\infty<\infty$,
and 
$f \in \mathcal{C}_{b}^\infty(\overline{\IR}^d)$, define the 
function $G_f$ by 
$G_f(\eta):=G (\langle f, \eta \rangle)$.
Let $\Pgen^N$ be the generator given by
\begin{equation}
\begin{aligned}
    \Pgen^N G_f(\eta)
    &:=
    G'(\langle f, \eta \rangle)
        \theta \bigg\langle
        \gamma(x, \eta)
            \int f(z) r(z,\eta) q_\theta(x,dz)
        -
        f(x)\mu_\theta(x, \eta),
        \eta(dx) \bigg\rangle
    \\&\qquad {}
    + \frac{1}{2} G''(\langle f, \eta \rangle)
    \frac{\theta}{N}
    \bigg\langle
        \gamma(x, \eta) \int f^2(y) r(y, \eta) q_\theta(x, dy) + f^2(x) \mu_\theta(x, \eta),
    \eta(dx) \bigg\rangle .
\end{aligned}
\end{equation}
A process $(\eta^N_t)_{t \geq 0}$ 
satisfies the martingale characterization of Definition~\ref{defn:mgale_construction}
if and only if it is a solution 
to the $(\Pgen^N, \eta_0)$-martingale problem, i.e.,
if for all such test functions 
$$
    M_t :=
    G_f(\eta^N_t) - G_f(\eta^N_0)
    - \int_{0}^{t}\Pgen^N G_f(\eta^N_s)ds
$$
is a martingale (with respect to the natural $\sigma$-field).

Furthermore, let $\Pgen^\infty$ be the generator given by
\begin{equation}
    \label{eq: Limit Generator Definition}
\begin{aligned}
\Pgen^{\infty} G_f(\eta)
    &:= G'(\langle f, \eta \rangle)
                   %\times 
\left\{
                   \big\langle
                        \gamma(x, \smooth{\gamma} \eta(x))
                            \mathcal{B}\left(
                            f(\cdot) r(\cdot, \smooth{r} \eta(\cdot))
                            \right)(x)
                    +
                    f(x)
                        F(x, \smooth{F} \eta(x)),
                        \eta(dx)
                    \big\rangle
                   \right\}\\
               &\qquad {}
               + \frac{\alpha}{2} G''(\langle f, \eta \rangle)
                  %\times 
\left\{
                  \big\langle
                    2\gamma\left( x, \eta \right)
                    r\left(x,\eta \right)
                    %+\mu\left(x,\eta \right)
                    f^2(x),
                    \eta (dx)
                    \big\rangle 
                  \right\}.
\end{aligned}    
\end{equation}
A process $(\eta^{\infty}_t)_{t \geq 0}$ 
satisifes the martingale characterization of equations~\ref{eqn:limiting_mgale_problem}
and~\ref{eqn:limiting_mgale_variation}
if and only if it is a solution 
to the $(\Pgen^{\infty}, \eta^\infty_0)$-martingale problem, i.e.,
if for all such test functions 
$$
    M_t :=
    G_f(\eta^{\infty}_t) - G_f(\eta^\infty_0)
    - \int_{0}^{t}\Pgen^{\infty}G_f(\eta^{\infty}_s)ds
$$
is a martingale (with respect to the natural $\sigma$-field). 
\end{lemma}

@@

% % % % % % % % % % % % %
\section{Lookdown Proofs}
    \label{sec:lookdown_proofs}

@@

\begin{lemma}
        \label{lem:h_containment}
    Let $h$ be a positive, continuous, nonincreasing, differentiable function on $[0, \infty)$
    such that
    $\int_0^\infty \int_u^\infty h(v) dv du$,
    $\int_0^\infty u^2 |h'(u)| du$,
    and $\int_0^\infty h(u)^2 du$
    are all finite,
    Suppose that Assumptions~\ref{def:model_setup} hold,
    and that $\theta/N \to \alpha$ and $\lp_0^N \to \lp_0$ weakly as $N \to \infty$,
    where each $\lp_0^N$ is conditionally uniform given $\eta_0^N$
    in the sense of \eqref{eqn:conditionally_uniform}
    and $\lp_0$ is conditionally uniform given $\eta_0$
    in the sense of \eqref{eqn:conditionally_poisson}.
    Then for any $T$ there exists a constant $K(T)$ such that for all $M > 0$,
    $$ 
    \limsup_{N \to \infty} \IP\left\{ \sup_{0 \le t \le T} \langle h, \lp^N_t \rangle > M \right\}
    <
    \frac{K(T)}{M} .
    $$
\end{lemma}

@@

\begin{lemma}
    \label{lem:compact containment hn}
    Suppose $f \in C(\bar \IR^d \times [0, \infty))$ and there is a $u_f$ such that
    $f(x, u) = 0$ for all $x$ and $u \ge u_f$.
    Under the assumptions of Lemma~\ref{lem:h_containment},
    for any $T$ there exists a constant $K(f,T)$ such that for all $M > 0$,
    $$ 
    \limsup_{N \to \infty} \IP\left\{ \sup_{0 \le t \le T} \langle f, \lp^N_t \rangle > M \right\}
    <
    \frac{K(f,T)}{M} .
    $$
\end{lemma}

@@

\begin{lemma}[Compact containment for $\lp$] \label{lem:compact containment lookdown}
    Let $f_1, f_2, \ldots$ be a sequence of functions each satisfying the conditions
    of Lemma~\ref{lem:compact containment hn}.
    Under the assumptions of Lemma~\ref{lem:h_containment},
    for any $T$ and $\delta > 0$ there exists a sequence
    $(C_1, C_2, \ldots)$ of finite constants such that
    \begin{align} \label{eqn:compact eqn lookdown}
    \limsup_{N \to \infty}
    \IP\left\{
        \sup_{0 \le t \le T} \langle f_k, \lp^N_t \rangle > C_k
        \text{ for some } k \ge 1
    \right\}
    < \delta .
    \end{align}
\end{lemma}

@@

\begin{definition}
    \label{def2: MP definition of pre-limit}
Let $F \in \mathcal{C}^{2}(\IR)$ and $f \in \mathcal{C}_{0}(\IR^d)$.
We define $\Pgen^N$ to be a generator
acting on test functions of the form
$F_f(\eta):=F (\langle f, \eta \rangle)$
such that 
\begin{equation}
\begin{aligned}
\Pgen^{N} F_f(\eta):=& \int_{\IR^d} \theta\gamma(x, \eta) \left\{\int_{\IR^d} \left\{F(\langle f, \eta \rangle + f(y)/N )-F(\langle f, \eta \rangle )\right\}r(y, \eta)q_{\theta}(x,dy)\right\}N\eta(dx)\\
&+\int_{\IR^d} \theta \mu_\theta(x, \eta) \left\{F(\langle f, \eta \rangle - f(x)/N )-F(\langle f, \eta \rangle )\right\}N\eta(dx).
\end{aligned}    
\end{equation}
In this case, our pre-limit model $(\eta^{N}(t))_{t \geq 0}$ is the solution to the Martingale Problem $(\Pgen^{N}, \eta_0)$, i.e. 
for all $F \in \mathcal{C}^{2}(\IR)$
and $f \in \mathcal{C}_{0}(\IR^d)$,
$$M_t:=F_f(\eta^{N}_t)-F_f(\eta_0)
-\int_{0}^{t}\Pgen^{N}F_f(\eta^{N}_s)ds$$
is a martingale, and the initial condition is distributed as a Poisson measure with mean measure $\eta_0$.
\end{definition}

@@

We may now rewrite $\mathcal{P}^NF(\langle f, \eta \rangle)$ as 
\small
\begin{equation} 
    \label{eq: Pre-Limit Generator Expanded}
\begin{aligned}
\Pgen^{N} F_f(\eta):=& F'(\langle f, \eta \rangle)\int_{\IR^d}  \theta\left\{\int_{\IR^d} \left\{f(y)\gamma(x, \eta) r(y,\eta) -f(x)\mu_\theta(x, \eta)\right\}q_{\theta}(x,dy)\right\}\eta(dx)\\
&+\frac{1}{2}\frac{\theta}{N}F''(\langle f, \eta \rangle)\int_{\IR^d} 
 \left\{\gamma(x, \eta)\int_{\IR^d} \left\{f^2(y) r(y,\eta) \right\}q_{\theta}(x,dy)+f^2(x)\mu_\theta(x, \eta)\right\}\eta(dx)\\
&+\frac{1}{6}\frac{\theta}{N^2}\int_{\IR^d}\left\{ 
F'''(w) \left\{\gamma(x, \eta)\int_{\IR^d} f^3(y) r(y,\eta) q_{\theta}(x,dy)\right\}-F'''(v)f^3(x)\mu_\theta(x, \eta)\right\}\eta(dx)
\end{aligned}    
\end{equation}
\normalsize
for some $w,v \in [\langle f,\eta \rangle - ||f||/N, \langle f,\eta \rangle + ||f||/N]$.

As $N\to \infty$, 
$\theta/N \to \alpha$, 
$\theta/N^2 \to 0$,
and 
$$\int_{\IR^d} f^m(y) r(y,\eta) q_{\theta}(x,dy) \to f^m(x)r(x, \eta)$$
for $m=2,3$,
the third term in Equation \eqref{eq: Pre-Limit Generator Expanded} vanishes
while the second term converges to
that of Equation \eqref{eq: Limit Generator Definition}.
Furthermore,
$\mu_\theta(x,\eta) = r(x,\eta)\gamma(x,\eta)-\frac{1}{\theta}F(x,\eta) \to r(x,\eta)\gamma(x,\eta),$
so $f^2(x)\mu_\theta(x,\eta) \to r(x,\eta)\gamma(x,\eta) f^2(x)$.

Finally, by Equation \eqref{mean measure},
\eqref{eqn:rewritten mean measure}, \eqref{eqn:near_critical} and
\eqref{limit of mean measure equation},
we have 
\begin{multline}
 \theta\left\{\int_{\IR^d} \left\{f(y)\gamma(x, \eta) r(y,\eta) -f(x)\mu_\theta(x, \eta)\right\}q_{\theta}(x,dy)\right\}
 \\
\to \gamma(x, \eta)                           \mathcal{B}\left(
                            f(\cdot) r(\cdot, \eta)
                            \right)(x)
                    +
                    f(x)
                        F(x, \eta),
\end{multline}
so comparing terms we have
\begin{equation}
\lim_{N\to \infty} |\mathcal{P}^{N}F\langle f, \eta \rangle - \mathcal{P}^{\infty}F\langle f, \eta \rangle| \to 0,   
\end{equation}
and so by Dominated Convergence Theorem,
we establish Equation 
\eqref{eq: Convergence of Spatial Generator}
which concludes our proof.
\end{proof}
